%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MSc Robotics, Systems and Control} % Degree
    {ETH Zurich} % Institution
    {Zurich, Switzerland} % Location
    {09/2022 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item Semester project: \textit{Altitude Estimation for UAV Operations Over Water - Integration and Testing of LiDAR and
        Radar Distance Sensors} under the supervision of Dr. Guillaume Ducard at the Institute for Dynamic Systems and Control (IDSC) group of Prof. Onder. I integrated and tested LiDAR and radar range finders with the goal of achieving reliable altitude measurements for PX4-powered UAVs operating over water. This involved assembling a custom PX4 quadcopter testing platform using FPV drone hardware from scratch, determining optimal radar parameters in ground-based tests, developing a sensor driver for PX4, flight testing over a lake, and analyzing test data using Python.
        \item Master's thesis: \textit{Agile Subject Tracking for Aerial Cinematography} under the supervision of Jiaxu Xing and Angel Romero at the Robotics and Perception Group (University of Zurich) led by Prof. Davide Scaramuzza. This work involved extending the "Flightmare" quadrotor RL environment (C++) for tracking subjects and avoiding obstacles. I also integrated Adversarial Motion Priors (AMP) into Stable Baselines3's PPO implementation using PyTorch and created an extensive debugging suite using Matplotlib, Rerun.io and Habitat-Sim. Furthermore, I extended the "Agilicious" framework for the simulation and real-world deployment of my trained policies using ROS. The policies were tested with a Vicon motion capture system and a FPV racing quadrotor platform.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {MSc Semester Exchange Program} % Degree
  {National University of Singapore} % Institution
  {Singapore} % Location
  {01/2023 - 05/2023} % Date(s)
  {
  }

%---------------------------------------------------------
  \cventry
    {BSc Mechanical Engineering} % Degree
    {ETH Zurich} % Institution
    {Zurich, Switzerland} % Location
    {09/2018 - 08/2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item GPA: 5.5/6.0 (approx. top 4\% of 207)
        \item Student project: \textit{Dyana - Dynamic Quadrupedal Animatronic} - A quadrupedal robot developed by an interdisciplinary team of 14 students from multiple Swiss universities. Dyana is capable of dynamic motions and conveys a unique, life‑like impression through its feline appearance. The project was hosted by the Robotics System Lab (RSL) led by Prof. Marco Hutter and was supported by several industry sponsors. More info from the \href{https://www.youtube.com/watch?v=--waMaVgZAg}{roll-out presentation (English subtitles) \ExternalLink}.
        \item Bachelor's thesis: \textit{Low‑ and High‑Level Control for Testing Single Legs of the Quadrupedal Animatronic Dyana} in collaboration with Marco Trentini and under the supervision of Fabian Tischhauser and Marcus Montenegro at the RSL. We developed a ROS 1 (C++) framework for dynamic testing of robotic legs using virtual model- and inverse dynamics control. It allowed us to test the mechanical integrity of the front and hind legs of \textit{Dyana} in a wall-mounted linear guide rail setup and evaluate the commercially available \textit{T-MOTOR AK10-9} actuators used.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {International Baccalaureate (IB) Billingual Diploma} % Degree
  {Leipzig International School} % Institution
  {Leipzig, Germany} % Location
  {08/2016 - 05/2018} % Date(s)
  {
    \begin{cvitems}
      \item Score: 42/45 (top 4.54\% worldwide)
      \item Higher level subjects: Mathematics, Physics, English (B)
      \item Standard level subjects: Chemistry, Geography, German (A)
      \item Valedictorian
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {International General Certificate of Secondary Education (IGCSE)}
  {Leipzig International School}
  {Leipzig, Germany}
  {08/2014 - 06/2016}
  {
    \begin{cvitems}
      \item {Top of the year group}
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}
